SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$, in Section \ref{section-sty} we
discussed the example of YGC input encoding, and in Sections
\ref{section-metalang} and \ref{section-metaty} we presented and
discussed the example of gates in the GMW protocol for binary
circuits. In this section we present an extended example of arithmetic
circuits with multiplication gates defined using Beaver triples
\cite{evans2018pragmatic}. We first define a compositional gate
library in $\metaprot$ with correctness conditions defined using the
Hoare logic developed in Section \ref{section-metalang}, along with a
small example circuit.  Then we will extend the library with type
annotations illustrating the use of share types developed in
Sections \ref{section-sty} and \ref{section-metaty} to enforce
confidentiality properties. Last, we will extend the base library
with additional pre and postcondition annotations to enforce
integrity properties supported by BDOZ/SPDZ style MACs
\cite{SPDZ1,SPDZ2,BDOZ,10.1007/978-3-030-68869-1_3}.

@@

>>>>

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$, in Section \ref{section-sty} we
discussed the example of YGC input encoding, and in Sections
\ref{section-metalang} and \ref{section-metaty} we presented and
discussed the example of gates in the GMW protocol for binary
circuits. In this section we present an extended example of 2-party
arithmetic circuits with multiplication gates defined using Beaver triples
\cite{evans2018pragmatic}. We first define a compositional gate
library in $\metaprot$ with correctness conditions defined using the
Hoare logic developed in Section \ref{section-metalang}, along with a
small example circuit.  Then we will extend the library with type
annotations illustrating the use of share types developed in
Sections \ref{section-sty} and \ref{section-metaty} to enforce
confidentiality properties. Last, we will extend the base library
with additional pre and postcondition annotations to enforce
integrity properties supported by BDOZ/SPDZ style MACs
\cite{SPDZ1,SPDZ2,BDOZ,10.1007/978-3-030-68869-1_3}.

@@

In this code we use a convention where shared values $\ttt{x}$ are
represented as a 3-tuple of values, MAC, and keys, where the value and
MAC of client \ttt{1} are $\ttt{m[x++"s"]@1}$ and $\ttt{m[x++"m"]@1}$
respectively, and the corresponding key is $\ttt{m[x++"k"]@2}$ is held
by client \ttt{2}. The correctness condition of this 3-tuple is
$\ttt{MACOK}(x,2,1)$. The same is true symmetrically, so $\ttt{MACed}$
establishes both sides of the correctness condition.  In general,
these are used in gate preconditions to assume that the MAC conditions
hold for input shares, and output shares are $\ttt{MACed}$. The
homomorphic properties that preserve $\ttt{MACed}$ness, especially in
\ttt{mult}, are perhaps even more complex than the algebraic
correctness of gates, so it is very beneficial to verify them
compositional especially for large circuits.

Our code is written so that share MACs are checked for when they are
\ttt{open}ed by both clients, specified by the appropriate
$\ttt{assert}$ included in the protocol. This ensures malicious
security of secure openings and outputs. As is standard in BDOZ/SPDZ,
we assume that input values, MACs, and keys are distributed to clients
by a pre-processing protocol.
